Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-02 paper.tex
Removed gnuplot-based frame rates chart
Added a title to the performance chart
Rearranged datasets in performance chart
Added chart for performance results from desktop

\begin{figure}
\centering
\includegraphics{frame-rates.pdf}
\label{frame-rates}
\end{figure}

\begin{figure}
\centering
\begin{tikzpicture}
\begin{axis}[
    xlabel=Samples,
    ylabel=Frames Per Second]
\addplot coordinates {
  (100, 22)
  (200, 10)
  (300, 7)
  (400, 5)
  (500, 4)
};
\addlegendentry{Slicing (attributes)}
\addplot coordinates {
  (100, 20)
  (200, 10)
  (300, 7)
  (400, 5)
  (500, 4)
};
\addlegendentry{Boolean XOR}
\addplot coordinates {
  (100, 20)
  (200, 10)
  (300, 6)
  (400, 4)
  (500, 4)
};
\addlegendentry{Depth-masking}
\addplot coordinates {
  (100, 6)
  (200, 3)
  (300, 2)
  (400, 1)
  (500, 1)
};
\addlegendentry{Slicing (uniforms)}
\end{axis}
\end{tikzpicture}
\caption{
Chart showing performance measurements as number of samples varies.  The slicing
with attributes, boolean XOR, and depth-masking methods are all about the same,
while the slicing with uniforms method lags behind considerably.
}
\end{figure}

>>>>

\begin{figure}
\centering
\begin{tikzpicture}
\begin{axis}[
    title=2.2 GHz i7 with AMD Radeon HD 6750M,
    xlabel=Samples,
    ylabel=Frames Per Second]
\addplot coordinates {
  (100, 20)
  (200, 10)
  (300, 6)
  (400, 4)
  (500, 4)
};
\addlegendentry{Depth-masking}
\addplot coordinates {
  (100, 20)
  (200, 10)
  (300, 7)
  (400, 5)
  (500, 4)
};
\addlegendentry{Boolean XOR}
\addplot coordinates {
  (100, 6)
  (200, 3)
  (300, 2)
  (400, 1)
  (500, 1)
};
\addlegendentry{Slicing (uniforms)}
\addplot coordinates {
  (100, 22)
  (200, 10)
  (300, 7)
  (400, 5)
  (500, 4)
};
\addlegendentry{Slicing (attributes)}
\end{axis}
\end{tikzpicture}
\caption{
Chart showing performance measurements as number of samples varies.  The slicing
with attributes, boolean XOR, and depth-masking methods are all about the same,
while the slicing with uniforms method lags behind considerably.
}
\end{figure}

\begin{figure}
\centering
\begin{tikzpicture}
\begin{axis}[
    title=3.0 GHz P4 with NVIDIA GeForce 8500 GT,
    xlabel=Samples,
    ylabel=Frames Per Second]
\addplot coordinates {
  (100, 10)
  (200, 6)
  (300, 4)
  (400, 3)
  (500, 2)
};
\addlegendentry{Depth-masking}
\addplot coordinates {
  (100, 13)
  (200, 7)
  (300, 5)
  (400, 4)
  (500, 3)
};
\addlegendentry{Boolean XOR}
\addplot coordinates {
  (100, 18)
  (200, 9)
  (300, 6)
  (400, 5)
  (500, 4)
};
\addlegendentry{Slicing (uniforms)}
\addplot coordinates {
  (100, 15)
  (200, 8)
  (300, 5)
  (400, 4)
  (500, 3)
};
\addlegendentry{Slicing (attributes)}
\end{axis}
\end{tikzpicture}
\caption{
Chart showing performance measurements as number of samples varies.  Here the
slicing with uniforms method is fastest, followed by the slicing with attributes
method, and the Boolean XOR method.  The depth-masking method is slowest.
}
\end{figure}
